Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review

### 2023-06-23 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Removed the device in ggsave to prevent confusion

# Save to github
ggsave(filename = "publications_per_year.tiff",
       plot = publications_per_year_plot,
       device = 'tiff',
       path = figs_dir
       )

# Save to dropbox folder
ggsave(filename = "fig2_publications_per_year.png",
       plot = publications_per_year_plot,
       device = 'tiff',
       path = dropbox_figs_dir
       )
```

>>>>

# Save to github
ggsave(filename = "publications_per_year.tiff",
       plot = publications_per_year_plot,
       path = figs_dir
       )

# Save to dropbox folder
ggsave(filename = "fig2_publications_per_year.png",
       plot = publications_per_year_plot,
       path = dropbox_figs_dir
       )
```
